Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-07 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{blue}{In this paper, which audience is targeted to be from the software verification area, we decided to use a higher-level explanation about the PV sizing. The sizing process involves a set of eighteen equations related to the electrical engineering area, which is detailed online.\footnote{\url{https://tinyurl.com/yck7dfxt}} The flowchart pictured in Fig.~\ref{fig:flow} is the overview of the steps that must be taken to size a stand-alone PV system.}
%
\begin{figure}[h]
\fbox{\includegraphics[width=0.9\textwidth]{flowchart}}
\centering
\caption{\textcolor{blue}{High level description of stand-alone PV system sizing process.}}
\label{fig:flow} 
\end{figure}

\textcolor{blue}{On the left side of Fig.~\ref{fig:flow}, we can visualize the needed \textbf{inputs} to size a PV system. There exist requirements from the house to be electrified; in particular, there exist design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}. Related to the equipment list, the designer can use a few equipments or a vast one. We can also decide not to adopt the commercial equipment list. However, the result is a PV sizing of specific power, current, or voltage values, and usually just close to original equipment, which can be found in the market. This possibility has the drawback of possible incompatibility among equipment when the real one is bought and deployed.}

\textcolor{blue}{There exist specific steps that aim the calculation of some variables and others related to the electrical compatibility validation among equipment items, both enumerated from \textbf{i} to \textbf{xiv}, as illustrated in Fig.~\ref{fig:flow}; those represent different shades of gray of the rectangle boxes. The start point is usually a candidate list of PV panels, charge controller, battery, and inverter, as indicated at the top of the flowchart. The arrows, on the right side, show a point where some specific item is validated. The diagram does not show the returning location. However, if the candidate item is not compatible with others or does not meet some requirement, it must be changed to follow the indicated flux. The last rectangle box checks the inverter electrical compatibility with the DC-bus voltage, with the required AC voltage from the outlet. Besides, the inverter specified power must be lower than the charge controller power to avoid it from burning by overcharge. At the end of the flowchart, all the items are defined, and the PV sizing is finished.}

@@

\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) are not the same. Therefore, the comparison must take this issue into account.}

@@

Our synthesis technique was developed and used open-source software verifiers and the environment, in contrast to the optimization and simulation tools used in this work. We have also observed that state-of-the-art software verifiers are doing an excellent job of solving hard verification conditions based on the underlying SAT/SMT solvers. Lastly, the use of data from real deployed systems in Brazil and the validation through PVsyst was essential to validate the comparison. \textcolor{blue}{Now that we proved that our technique has a promising result for PV system sizing optimization, our focus for future work will be the improvement with the search mechanism used in the {\sc Verify} phase of our synthesis technique, to speed up the time to respond. We plan to use parallel binary search~\cite{TrindadeDJISC17} or even a solver that is specific to perform optimization with model checking as $\nu Z$~\cite{BjornerPF15}.}

>>>>

\textcolor{blue}{Since this paper's audience is targeted to be from the software verification area, we decided to use a higher-level explanation about the PV sizing. The sizing process involves a set of eighteen equations related to the electrical engineering area, which is detailed online.\footnote{\url{https://tinyurl.com/yck7dfxt}} Fig.~\ref{fig:flow} illustrates the overview of the steps that must be taken to size a stand-alone PV system.}
%
\begin{figure}[h]
\fbox{\includegraphics[width=0.9\textwidth]{flowchart}}
\centering
\caption{\textcolor{blue}{High level description of stand-alone PV system sizing process.}}
\label{fig:flow} 
\end{figure}

\textcolor{blue}{On the left side of Fig.~\ref{fig:flow}, we describe the needed \textbf{inputs} to size a PV system. There exist requirements from the house to be electrified; in particular, we have the design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}. Concerning the equipment list, the designer can use a few equipments or a vast one. We can also decide not to adopt the commercial equipment list. However, the result is a PV sizing of specific power, current, or voltage values, and usually just close to original equipment, which can be found in the market. This possibility has the drawback of possible incompatibility among equipment when the real one is bought and deployed.}

\textcolor{blue}{There exist specific steps that aim the calculation of some variables and others related to the electrical compatibility validation among equipment items, both enumerated from \textbf{i} to \textbf{xiv}, as illustrated in Fig.~\ref{fig:flow}; those represent different shades of gray of the rectangle boxes. The start point is usually a candidate list of PV panels, charge controller, battery, and inverter, as indicated at the top of the flowchart. The arrows, on the right side, show a point where some specific item is validated. The diagram does not show the returning location. However, if the candidate item is not compatible with others or does not meet some requirement, it must be changed to follow the indicated flow. The last rectangle box checks the inverter electrical compatibility with the DC-bus voltage, with the required AC voltage from the outlet. Besides, the inverter specified power must be lower than the charge controller power to avoid it from burning by overcharge. At the end of the flowchart, all the items are defined, and the PV sizing is finished.}

@@

\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) are not the same \textcolor{red}{add citation}. Therefore, the comparison must take this issue into account.}

@@

Our synthesis technique was developed and used open-source software verifiers and the environment, in contrast to the optimization and simulation tools used in this work. We have also observed that state-of-the-art software verifiers are doing an excellent job of solving hard verification conditions based on the underlying SAT/SMT solvers. Lastly, the use of data from real deployed systems in Brazil and the validation through PVsyst was essential to validate the comparison. \textcolor{blue}{We have shown that our technique has a promising result for PV system sizing optimization. Our focus for future work consists of improving the search mechanism used in the {\sc Verify} phase of our synthesis technique to speed up the overall time. We plan to use parallel binary search~\cite{TrindadeDJISC17} or even a solver that is specific to perform optimization with model checking as $\nu Z$~\cite{BjornerPF15}.}
